---
title: "How Much Can We Trust Our Timers ?"
author: David Napravnik
output: html_document
---


```{r}
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggplot2")) install.packages("ggplot2")
```


# PC specs:
- OS: Windows Home 10.0.19045
- Processor:	AMD Ryzen 7 5800HS, 3201 Mhz, 8 Core(s), 16 Logical Processor(s)
- Installed Physical Memory (RAM):	24.0 GB

# Browsers:
- Chrome: Version 110.0.5481.178 (Official Build) (64-bit)
- Firefox: 110.0 (64-bit)
- Edge: Version 110.0.1587.63 (Official build) (64-bit)


# Protection:
Because of protection against timing attacks and fingerprinting,
performance.now() is coarsened based on site isolation status.r

url where `crossOriginIsolated=true`
https://stackblitz.com/edit/cors-corp-origin-isolated?file=browsersync.config.js


## Script to get `crossOriginIsolated`
``` javasccript
console.log({
  crossOriginIsolated
})
```


# The resolution and the granularity of the timers
```{r}

# Create data
datagranularity <- data.frame(
  method=c(
    "Chrome: Date.now()",
    "Firefox: Date.now()",
    "Edge: Date.now()",
    "Chrome: performance.now()",
    "Firefox: performance.now()",
    "Edge: performance.now()",
    "Chrome: performance.now() + crossOriginIsolated",
    "Firefox: performance.now() + crossOriginIsolated",
    "Edge: performance.now() + crossOriginIsolated") ,  
  resolution=c(
    1, 1, 1,
    0.1, 1.0, 0.1,
    0.005, 0.02, 0.005
    ),
  fills=c("chrome", "firefox", "edge","chrome", "firefox", "edge","chrome", "firefox", "edge")
  )


# Barplot
ggplot(datagranularity, aes(y=method, x=resolution, fill=fills)) + 
  geom_bar(stat = "identity")+
  xlab("Granuality in ms (lower is better)")+
  ylab("Browser: method")+
  geom_text(aes(x = .5, label = resolution)) +
  ggtitle("Granuality of time measure methods across browsers")

```

Best resolution we can get is 0.005ms.

## Script to measure increment size in timer method.

``` javasccript
let out = []
let last = performance.now();
while (true) {
  const now = performance.now();
  if (now === last) continue;
  out.push(now - last)
  last = now;
  if (out.length >= 10) break;
}
console.log("resolution: ", out.sort((a, b)=>a-b).map((value) => Math.round(value * 10000) / 10000))
```


# The overhead of the timer access
```{r}

# Create data
dataoverhead <- data.frame(
  method=c(
    "Chrome: performance.now()",
    "Chrome: Date.now()",
    "Firefox: performance.now()",
    "Firefox: Date.now()",
    "Edge: performance.now()",
    "Edge: Date.now()"),
  resolution=c(
    239.21, 75.01,
    203.92, 185.13,
    203.82, 72.17
    ),
  fills=c("chrome", "firefox", "edge","chrome", "firefox", "edge")
  )
  

# Barplot
ggplot(dataoverhead, aes(y=method, x=resolution, fill=fills)) + 
  geom_bar(stat = "identity")+
  xlab("Overhead in ns (lower is better)")+
  ylab("Browser: method")+
  geom_text(aes(x = 100, label = resolution), position = position_dodge(.9)) +
  ggtitle("Overhead of time measure methods across browsers")

```

## Script to measure increment size in timer method.

``` javasccript
const before2 = performance.now();
for (let i = 0; i < 100 * 1000 * 1000; i++) {
	const a = 0;
}
const before = performance.now();
for (let i = 0; i < 100 * 1000 * 1000; i++) {
  const a = performance.now();
}
const after = performance.now();
for (let i = 0; i < 100 * 1000 * 1000; i++) {
  const a = Date.now();
}
const after2 = performance.now();
const overhead = Math.round(before - before2);

console.log("performance.now: ", Math.round(after - before - overhead)/100 + " ns")
console.log("Date.now: ", Math.round(after2 - after - overhead)/100 + " ns")
```

# The stability of the timer
because resolution of timer is 1.000 times less than overhead,
any meassurement of these methods must be repeated and cant be measured without warm up.






