\subsection{Other Dormitories}
\budovaAdresa{
    The student residence Na Větrníku, Na Větrníku 1932, 162 00 Prague 6
    The student residence Kajetánka, Radimova 12, 169 00 Prague 6
}
While the student residence 17. listopadu has nice rooms but unpleasant surroundings, the student residence \textit{Na
Větrníku} (also called Větrák) has it the other way around -- there are nice surroundings and a park near the dormitory bud the rooms are small and ugly. On the other hand, it is very cheap.
The student residence \textit{Kajetánka} (also called Kajka) is located about 20 minutes away from Na Větrníku. Many students of medicine and computer science stay there.

\budovaAdresa{The student residence Areál Hostivař, Weilova 2, 100 00 Prague 10}
This dormitory is meant to accommodate the students of Erasmus or Erasmus+. There are single and double rooms (the price differs). The double rooms have its own toilets and there are also toilets on each floor. Some of the rooms but do not have its own toilets (the price also differs).
There is always one kitchen on each floor. It is a good place for meeting new people.
There is a study room, copy machine, coffee and tea vending machine and also a normal vending machine in the entrance hall. It is also possible to buy sandwiches at the reception.
The laundry room is located in the basement of the building 1.
There is a hairdresser and pizzeria in the complex of the dormitory buildings (on the terrace of the building A) and you can also find Charles University Sports Center in the vicinity, with a swimming pool, tennis courts and indoor hall.
The residents of the dormitory can connect to the university wifi network called eduroam. Your login name is: name@cuni.cz or isicnumber@cuni.cz. You should be able to set your password in the CAS system.

\budovaAdresa{
    The students residence Vltava, Chemická 953, 148 28 Prague 4 - Jižní Město
    The student residenc Otava, Chemická 954, 148 28 Prague 4 - Jižní Město
}
Someone says that these dormitories are good value for money, someone says that they are a bit far away from the city center. 
Lots of students of VŠE (University of Economics) stay here.

\budovaAdresa{The student residence Budeč, Wenzigova 20, 120 00 Prague 2}
The student residence \textit{Budeč} is located fairly close to Karlov. It is a small dormitory in the city center (7 min walk from I. P. Pavlova) and has about 225 residents who mostly know each other and organize small parties (and even big ones, about four times a year).
The rooms are a bit smaller and not all of them are the same size, some double rooms are as big as the rooms for three. 
The first three floors were reconstructed in 2017. The only disadvantage of this dormitory might be that all of the residents of one floor have a collective kitchen, two collective toilets and showers. Warning: the toilets and showers for men and women are not separated.
However, they are cleaned daily so do not worry about that.
One big advantage of this dormitory is its refectory, one of the best of the Charles University refectories.
Every floor has its own study room where you often find the students of medicine, law and philosophy. 
How can you get to MFF? Albertov is a 6 min walk. If you take the tram no. 22 from the I. P. Pavlova, you can get to Malostranské náměstí in $\pm$ 17 min (or in 14 min if you are in a hurry and use the metro). It takes about 20 min by the metro and bus to get to Trója.
Generally speaking, if you want to go anywhere, just set out half an hour earlier and you should get there in time.
Unfortunately, Hostivař is a bit far away even from this place. Just take the tram no. 22 from I. P. Pavlova or go two stops by metro to Hlavní nádraží and then go by train (runs once every half an hour). 
But the safest way is to take a book with you, get on the tram no. 22 and not hurry anywhere.

\budovaAdresa{The student residence Švehlova, Slavíkova 22, 130 00 Prague 3}
\textit{The student residence Švehlova} (also called Švehlovka) is also located in a nice historical building but it is larger then Budeč and has a theatre instead of a refectory.
It is situated near náměstí Jiřího z Poděbrad so it is not very close to any of the MFF's building but at the same time it is not that far away (including Hostivař!).


The Charles University has eleven dormitories in total just in Prague. All of them have different facilities and rooms, from single rooms to rooms for five people.
We will not mention all of them because we actually do not know much about some of them but we still believe that staying at the dormitory is a valuable experience and a part of the student's life and you should not miss it.