\subsection{Faculty buildings}
The Faculty of Mathematics and Physics is based at several locations in Prague.
Most often you will visit one of these four locations: Karlov (where the Dean's
departments can be found and the students of Physics have most of their lectures
there), Malá Strana (where most of the students of Computer Science have their
lectures), Karlín (the students of Mathematics usually have their lectures
there) and Troja (there are labs and lecture rooms of the students of Physics
and there are also lecture rooms used for the purposes of language education).


\subsubsection{Karlov}
Two neighbouring faculty buildings are based there, in the street Ke Karlovu.

\budovaInfo{Ke Karlovu 3, Prague 2}
{Mathematicians, physicists}
{It houses the Dean's departments and Student Affairs Department and you can get
your ISIC card sorted out in the basement.
M1 is our largest lecture room and physics practical classes take place there.}
{Names of the rooms start with the letter \uv{M} (M1, M2, M3, M5 a M6).}
{The refectories Albertov and Budeč are the closest ones. You might use the jug
kettle or microwave located in the lab.}
{Bike-stands are in the courtyard.}

\budovaInfo{Ke Karlovu 5, Prague 2}
{Physicists}
{It houses the Institute of Physics of Charles University and you can find the
Foucault pendulum there.}
{Names of the rooms start with the letter \uv{F} (F1, F2 a KFK)}
{The closest refectories are Albertov and Budeč. You might use the jug kettle or
microwave located in the lab of the building M.}
{Bike-stands are in the courtyard of the building M.}

\subsubsection{Malá Strana}

\budovaInfo{Malostranské náměstí 25, Prague 1}
{Computer scientists}
{The oldest and most beautiful faculty building. There is an 11th century
rotunda of St. Wenceslas and also Rotunda, the most important lab for the
students of computer science. The building is almost always locked because of
tourists, you need an ISIC card to enter.}
{Names of the rooms start with S \uv{S} (S1, S3, \dots, S11), four IT classrooms
(SW1,
SW2, SU1, SU2), Rotunda, lots of other lecture rooms. The whole building is
often called MS (short for Malá Strana).}
{The restaurant Profesní dům with student discounts is located in the basement
of this building. Other options include McDonald's, Biomarket Vacek and a
chinese restaurant near Karlův most. If you follow the tramway for about 100 m
in the direction of Újezd (not through the tunnel), you will come across another
chinese restaurant and Subway.
The closest refectory is located in the building of the Faculty of Law -- take
the tram no. 15 or just walk across Mánesův most. There is also a school canteen
in Dražického náměstí.
A microwave is located on the 4th floor of this building (in front of S1) at the
end of the left corridor.
}
{Bike-stands are in the left corridor (in front of SW2) and in the courtyard.}


\subsubsection{Karlín}

\budovaInfo{Sokolovská 83, Prague 8}
{Mathematicians}
{The best room of MFF is situated in the basement --\textit{Respirium} and it
has a jug kettle, microwave and a place to relax. The shop of MatfyzPress is
based on the ground floor.}
{\uv{K} (K1--K12) + other lecture rooms.}
{The refectory Jednota is just a few stops by tram away. There are also lots of
fast food restaurant near the metro station and the shops Billa and Lidl are
also based in the street.}
{A stand in the courtyard (ring the bell for the reception).}

\subsubsection{Troja}
There is a whole building complex in Troja -- one high rise building, four low
rise buildings and one is being constructed. The main building is marked by T,
the high rise building by A, the building of the heavy technology laboratories
by L, the building of the research and development workrooms by V and the last
one is the cryogenics laboratory with the letter C.
The building housing the IT classrooms is still being constructed and the works
should be finished at the end of 2019.
You can find a map of this complex at the end of the Cookbook.

\budovaInfo{V Holešovičkách 2, 180 00 Prague 8}
{Physicists}
{The Faculty of Nuclear Sciences
and Physical Engineering of the Czech Technical University in Prague is also
based there, then you can find \textit{Van der Graff Generator} and the nuclear
sciences' reactor VR1 (code name \textit{Vrabec} -- Sparrow in English) in the
building L. The whole complex (with the exception of the building C) is
interconnected by the underground corridors.}
{Names of the rooms start with the letters \uv{T}, \uv{A}, \uv{V}, \uv{C} a
\uv{L} (T1, T2, T5--T10,
VxxxJAZ) + other lecture rooms located in the departments}
{There is a buffet in the building T, other options include shops and
restaurants near Nádraží Holešovice or Bulovka. }
{There are stands in front of all buildings in this campus. You can also leave
your bike in the entrance hall of the building C, opposite the porter's lodge.}