\subsection{Labs}
The computer laboratories are called \textit{labs} for short. There is at least one in every faculty building, They are generally accessible by the students of Matfyz but there are also some computers belonging to the departments which only some of the students might use.

If you want to access the lab, you will need Charles University student card and a user account or an access to the SIS (Study Information System).
If you need to set up the account, you can apply for it in one of the labs and the account is established right away.
Every student of the Charles University might access the computers in Troja and Karlov. You log in with the same user name and password as if you tried to log in to SIS. 
Sometimes it is necessary to find the lab's administrator and undergo a training about the lab's specifics.

The labs may or might not be occupied depending on the time of the day, part of the semester and also the lab's location. Most people use the labs during the winter semester.
On the other hand, the lab in Karlov is usually empty because it is not easy to find it. Do not forget to follow the Dean's directive no. 4/2008 stating that you have to treat the computers well and that you cannot use illegal software or write abusive emails.

Every lab has a printer, the black and white printing costs 1 CZK for one A4, the colour printing from 5 to 15 CZK. Not all of the printers are able to print in colour.
Most of the labs also have a scanner.

Each of the labs has its own website, you can find the list here  \url{www.mff.cuni.cz/cs/vnitrni-zalezitosti/it-a-sluzby/pocitacove-laboratore}(CZ).

For more information about the labs check out the electronic version of the Cookbook:
 \url{www.matfyzak.cz/kucharka/index.php?title=Laby}(CZ).



\subsubsection{Alternatives}
It often happens that the computer lab is closed and your roommate needs the room to spend some joyful time with his girlfriend and sometimes it collides with the times you actually need to work.
If you have your own laptop, you can use the night study room in the National Library of Technology in Dejvice. It is opened any time, even when the library itself is closed, and there is wifi, electricity, toilets and vending machines.
However, you will need to make the registration some time during the day -- it costs 100 CZK per year.