\subsection{Important Refectories}
The refectories are the canteens of the Charles University. The food is paid for
with an ISIC card so you have to charge it in one of the refectories. You also
need to register yourself on your first visit (but this registration is then
valid for all of the Charles University refectories).
Your account will be set up and it will then enable you to pay or order meals
online (at least a day in advance). If you do not order your meals, you will
have to take anything that is left.

The price is about 50--80 CZK for students. You can usually choose from 4 meals
(at least one of them is vegetarian) and soup (single price 9.20 CZK), sometimes
you can also choose from more expensive (but luxury) meals.
The refectories are closed on weekends. Another way to feed yourself is to buy
subsidized sandwiches (for budget-friendly prices) at the dormitory receptions,
refectories and in some faculty buildings.


\subsubsection{Refectory Troja}
It is temporarily closed at the moment and it is not sure when it will reopen.
It has been substituted by a vending machine on the ground floor of the building
A but it is not really a sufficient replacement.

Once the refectory is opened, you will find it in the basement of the building A
(go down the stairs from the reception and turn left).


\subsubsection{Albertov (Albertov 7)}
It is located near the buildings in Karlov so it is very convenient for the
students of Mathematics (in their first year) and Physics. Althought the queues
are long, they tend to move quickly and you will most likely have no problem
with finding a place to sit.

The easiest way to get there from both of the faculty buildings in Karlov is to
take the path between these buildings and go straight ahead until you see a
building with a sign Menza on your right side.


\subsubsection{Budeč (Wenzigova 20)}
Another refectory in Karlov. It is noticeably smaller than the one in Albertov
so you might have some problems with finding a place to sit but they cook better
and the building was recently reconstructed.

The fastest way to get there from both of the faculty buildings is to go in the
direction of Nuselský most (which means turn right and then take left at the end
of the street), go through the pedestrian underpass, turn left and then right at
the nearest crossroads.
Another way how to get there from the faculty building is to turn left and then
right at the crossroads with Wenzigova street. The refectory is then located at
the end of the street.


\subsubsection{Jednota (Opletalova 38)}
The queues are often long but move fast. They cook well, the students of Matfyz
from Karlín usually go there or stop on the way to Karlov.
It is very spacious so you usually do not have to share your table with
strangers.

You can get there from Florenc by taking the tram to Masarykovo nádraží, then
walk in the direction of the tram, turn left at the first crossroad and then
right to Opletalova street. The refectory is located on the left side, almost at
the beginning of the street.
Or you can walk from Hlavní nádraží -- turn right and go down through
\uv{Šervůd} (park right in front of Hlavní nádraží) until you reach a crossroad.
Cross the street and continue straight ahead. The refectory is located on the
right side of the street.


\subsubsection{Arnošta z Pardubic (Voršilská 1)}
The refectory is being reconstructed, hopefully it will open at the beginning of
the summer semester 2019/2020.

Take the tram no. 22 from Malostranské náměstí to Národní divadlo. Then walk in
the direction of the tram, take the first street on the right and right past the
first \uv{crossroads} you will see a building with large wooden door -- the
refectory.

Take the tram or metro line B from Národní třída to the street Ostrovní (if you
went by the metro, go straight ahead across the tramway and take the little
street on the right side past the tram stop), then go straight ahead. Take the
second turn left and you will stand right in front of the refectory (the only
building on the right side of the street with large wooden door).


\subsubsection{Právnická (Nám. Curieových 7)}
Lots of beautiful female students eat their lunch there -- the students of law
and from the nearby Faculty of Arts. The refectory is located in the basement of
the building of the Faculty of Law. The food is satisfying, portions big, queues
are longer but they move fast.

Take the tram no. 8 from Karlín (and then the tram no. 15 at Náměstí Republiky)
or the tram no. 17 from the student residence 17. listopadu and go to the stop
Právnická fakulta (or Čechův most and then cross the river Vltava).
If you are travelling in the opposite direction, from Malostranská, just cross
over Mánesův most, turn left and walk along the riverbank until you reach the
building of the Faculty of Law.

Take the tram no. 15 from Malostranské náměstí in the direction of Malostranská
and get off at Čechův most, the refectory is lcoated at the other side of the
river. You can cross the bridge on foot or you can take the tram no. 17 on the
opposite side of the street.


\subsubsection{Hostivař (Weilova 1144/2)}
You will stop here mostly on your way to your PE class (it is usually not a good
idea to stop there on your way there).
Go in the opposite direction than that of the railway station from Nádraží
Hostivař until you reach the student residence Hostivař. The refectory is huge
so finding a place to sit will not be difficult and the food is also pretty
good.