\subsection{Buildings not beloning to the faculty}
The faculty buildings are not the only ones you will visit during your study. The most important of them is probably the Charles University Sports Center where most of the PE classes take place. 
Another buildings worth mentioning are Karolinum -- historical seat of the university that you will visit during the matriculation -- or the boathouse in Malá Chuchle where the canoeing classes take place.


\subsubsection{SCUK (Charles University Sports Center) Hostivař}
\budovaKratce{Bruslařská 10, 102 00 Prague 10 - Hostivař}
{PE teachers}
Its first floor houses the departments of physical education of some faculties, ours is located in the back.

You can find most of the changing rooms if you enter the building, go down the stairs and turn left (women's changing rooms are on the right, men's on the left). 
If you want to go to the swimming pool, borrow a padlock from a lady in the window facing the stairs and go to the changing rooms right next to this window. 
You need to have your own padlock for locking your locker in the other changing rooms.

The location of this building might become a reason you will hate PE because it is on the other side of Prague than all other faculty buildings.


\subsubsection{Karolinum (Charles University Rector's Departments)}
\budovaKratce{Ovocný trh 5, 116 36 Prague 1}
{Bureaucrats}
Needles to say, the rector's departments does not belong to the faculty. It is similar to our Dean's departments but influences the whole university (meaning more than 50 000 students).
Two events usually take place in the famous ancient \textit{Karolinum}: \textit{matriculation ceremony} (for the first year students, we recommend you to attend it at least once) and \textit{graduation ceremony} (just for master students who successfully graduated).


\subsubsection{Boathouse Malá Chuchle}
\budovaKratce{Strakonická Prague 5 - Malá Chuchle}
{PE teachers}
If you choose to visit canoeing classes, you will commute to Malá Chuchle in the first month of the winter semester and the last month(s) of the summer semester. You will squeeze in the swimming pool in Hostivař with the swimmers during the winter.