\subsection{Organizational Structure}

The structure of the faculty is fairly complicated so we will describe it only briefly.


\subsubsection{Charles University}
Although many people do not really realize it, Matfyz is a part of the Charles University (which you have probably already heard of). The future philosophers, lawyers, biologists and others also study there. The university is run by \textit{the Rectorate} whose head is called \textit{the Rector} (prof. Tomáš Zima from the First Faculty of Medicine since February 2014) and he is advised by his team of \textit{the Vice-Rectors}. You most likely will not meet them directly except for some very exceptional events. 


\subsubsection{Faculty of Mathematics and Physics}
The head of the faculty is called \textit{the Dean}. 
Because dealing with the everyday life's problems of the whole faculty is an impossible task to do for just one person, the Dean is advised by the Advisory Board. 
It consist for example of eight \textit{Vice-Deans} (each of them takes care of one part of faculty's life) and \textit{the Head of Administration} who takes care of the faculty's economic activities.
The Dean and his Advisory Board together constitute the management of the faculty. The Dean for the period of September 2012 – 2020 is prof. Jan Kratochvíl. 
 \textit{The Scientific Council} consists of the top experts in the field working for the faculty. It is responsible for the authorization of the study plans and its members debate the appointment of new docents and professors, besides other things.


\subsubsection{Senate}
Another key authority of the faculty is \textit{the Academic Senate of MFF UK} which has 25 members – 16 of them together compose \textit{the Staff Chamber} and 9 of them \textit{the Student Chamber}.
The Senate significantly influences most of the events occurring during the academic year such as electing the Dean or drawing up the budget. 
At the end of each academic year the students elect three representatives to the Student Chamber for a three-year term. The sessions of the Senate and their records are freely available. 
The students of Matfyz also elect two representatives to \textit{the Academic Senate of Charles University} every two years. 
This so-called Great Senate has more or less the same rights and duties as the faculty's senate but its authority includes the whole university (that means that the members of this Senate elect the Rector or approve the internal regulations of the Charles University which influence all faculties).


\subsubsection{Schools}
MFF UK is divided into three \textit{schools} – \textit{the School of Mathematics}, \textit{the School of Physics} and \textit{the School of Computer Science}. These schools consist of departments and each of them has its own Vice-Dean. 
Apart from these three schools there is also the Department of Language Education and the Department of Physical Education (which actually happens to be quite popular amongst our students). 
Also you can find here so-called \textit{Technical Support} (such as \textit{the Library} or \textit{the Reprographic center} in Karlín) and, of course, \textit{the Dean's Office} composed of many departments which an average student does not know and does not even have to; the only exception is the Student Affairs Department whose head is \textit{the Vice-Dean for Student Affairs} (doc. František Chmelík). We encourage you to contact him if you were to have any difficulties with your studies.