\subsection[SKAS]{SKAS (Student Chamber of the Academic Senate)}
It represents students and their interests in self-governance of the faculty.
It has 9 members elected at the end of the academic year by \textit{you,
students}. Three representatives are elected each year for a three-year term.
The duties of the SKAS include controlling the way the faculty is run (more than
one third of the votes in the Academic Senate is theirs) and presenting the view
of the students to the Senate and the dean.
Therefore, do not forget to vote!

You can always turn to the SKAS, especially if you have any difficulties with
your study (e.g. the teacher takes a lot of time to correct the tests etc.) or
if you need any information about the study and do not know who else to ask.
\textbf{Remember that most of the problems can be solved, you just have to start
solving them as soon as possible.}

The contacts and other information about the activities and organization of the
SKAS can be found on the notice board in every building or on the website
\url{skas.mff.cuni.cz}(CZ).

\subsubsection{Student evaluation}
The student evaluation is supposed to enable the students to evaluate the
performance of their teachers.
You should complete it as it will help the other students and sometimes even the
teachers. They usually do not intend to make faults.
Please write comments (either positive or negative). Your teachers as
well as the faculty management will certainly read them and sometimes also
react.

The evaluation always happens during the examination period. It has taken
different forms during the last years, currently you will fill out your
evaluation online in the SIS where you can also find the results of the previous
evaluations.