\subsection{Spolek Matfyzák}

The \textit{Spolek Matfyzák} is a group of the MFF’s students organising various events and helping other students -- its members are also the authors of this Cookbook. Any (even former) student of MFF or a person associated with Matfyz in any other way might become its member.

Its leader is called \textit{Náčelník} (``Chief") and he is surrounded by his \textit{Náčelnictvo}. There is also \textit{Rada starších} (``Council of Elders") that makes sure that everything happens according to the rules.
The website is \url{matfyzak.cz}(CZ) and you can reach them at spolek@matfyzak.cz or via Facebook.

Anyone can become a member, the members often change as students come and go.
\textit{Become an active member of Spolek Matfyzák!} If you like to organize various events, have inspiring ideas or you just want to chat with older students, this is the place to go. Just contact us. You will most definitely gain a lot of useful skills and make new friends.


\subsubsection{Beánie}
The \textit{Beánie} is a party held at the beginning of the semester.
The first year students become the ``proper students of Matfyz" during the ancient ``Jarníkův rituál" (``Jarník's ritual"). 
You can watch the cult movie Matfyzák and other movies created by the students of Matfyz, listen to the concerts of various bands and there are always some entertaining competitions and theatre plays. There is also the famous exhibition \textit{Matfyzák včera, dnes a zítra} (``the student of Matfyz yesterday, today and tomorrow") and you might buy some T-shirts with the logo of Matfyz and other items.
This event is meant mostly for the Czech students, but not exclusively and you are very much welcome to come. However, it is all in Czech so we recommend you to come with someone who can translate it for you.


\subsubsection{Matfyz Ball}
\textit{The Matfyz Ball} takes place in the beautiful Žofín ballroom. Every student tries to score some points with the teachers by showing his perfect dancing skills (because the examination period is coming and you never know what might be of use to you) or at least win some of the tombola prizes. 
You can buy the tickets a few weeks before the ball takes place in the library, at the dormitory or online. Book your tickets in advance as they usually sell out quickly.


\subsubsection{Other activities}
Besides these events we also organize a few others every year. Some of them take place at the student residence 17. listopadu -- e.g. \textit{KolejCup} (trivia quiz including lots of running) and \textit{Běh do schodů} (``Up the Stairs Run", it is probably clear what happens there, the all-time high is 1 min 36 sec).
Tour de Pub is another popular event -- more or less regular meetings in the pub where we drink beer or others drinks and just chat.
Spolek also tries to do some socially beneficial acts -- e.g. the members go donate blood together. Just regularly check our website or the notice boards at the faculty buildings and you will find out all the necessary information about the upcoming events.

Spolek also cooperates with other organizations, theatres (check our website for the discounts), sells T-shirts with the logo of Matfyz and other items (e-shop can also be found on our website) and manages this Cookbook.

\subsubsubsection{Activities of the university}
Apart from the MFF's events Spolek Matfyzák also participates in the events organized for all students of the Charles University, such as Studentský jarmark (``Student fair"). You can learn information about all of the things you can do while studying at the university, listen to the music, taste some great food and drinks and learn about other societies at the university.

Spolek Matfyzák also publishes invitations for other interesting university activities or lectures.


\subsubsection{Other societies and associations}
There are lots of other societies and associations at the university.There is also the Charles University Student Union (SU UK, \url{cssauk.cz}(CZ)) acts as a guide for university student organizations, facilitating communication and cooperation among them, developing a creative platform for active students, supporting the implementation of their ideas, and acting as a mediator providing information to all students about what is currently happening in the academic community.
Current events organized for the whole university are Studentský jarmark or Studentský majáles (``Student fair") and the CU Student Union also organizes discussions with famous people.