\subsection{Free Time}
There are many things to do in Prague in one's spare time.
There are many shops, sports venues, theatres (either amateur and National),
cinemas, pubs, sweet shops and basically almost everything you might even think
of.
Usually whenever you need to find something, you just ask Uncle Google and he
tells you whatever you need to know.
Therefore we do not intend to list all the available facilities from A to Z but
we would just like to offer you a few recommendations (most of them can be found
in the vicinity of the student residence 17. listopadu).


\subsubsection{Where to go near the student residence 17. listopadu}
Would you like to have a break or go for a walk? Sometimes you just want to go
for a hike, sit in a park or take your study books outside.
There are a few places near the dormitory that are worth mentioning.
\begin{itemize}
\item \textbf{Stromovka} – a large park extending from Výstaviště to the river
and also to Bubeneč. The trees there offer shade in the summer and there are
also a few ponds.
\item \textbf{Zoo Praha (Prague Zoo)} – 3,5 km away, it is possible to reach the
main entrance by walking along the river or by taking a bus no. 112. A few nice
new exhibits can be found there.
It takes almost a whole day to walk around the zoo and you should also take into
account that there will probably be lots of guests.
If you visit the zoo on Monday, you can usually get a student discount.
\item \textbf{Botanická zahrada Praha (Prague Botanical Garden)} – it is located
near the zoo and the daily student ticket costs 45 CZK (43 CZK if you have the
Lítačka card). The annual ticket costs 300 CZK and the entrance is free during
the winter.
The temperatures are very comfortable here even during the summer and the place
is suitable for studying.
\end{itemize}
If you just want to go for a walk, you can stroll along the right side of the
river in both directions.


\subsubsection{Sports facilities}
There is an aerobics room and a table tennis room in the basement of the
dormitory building. Both of them were closed at the time this handbook was
written because of the construction in progress in the building C but their
reopening is expected.
Once they are opened, It will be possible to visit them for free in exchange for
the dormitory ID card.
Another sport facility you can find in the basement is the gym. You need to pay
an annual token charge to be allowed to exercise there.
A grass area for playing frisbee and other sports is located east of the
dormitory but it is supposed to turn into a minipark and a multi-purpose
playground.
South of the dormitory parallel and horizontal bars can be found but they will
be also later replaced by an interconnection between the streets Povltavská and
Pátkova.
Some of the sport equipment can be borrowed at the reception in the building B.
Any news about the sport equipment appear on the website of dormitory council.

We also should not forget to mention a nice cycleway along the river. It starts
right in front of the dormitory and heads west through the zoo and ends up in
Klecánky (then you can continue to e.g. Kralupy nad Vltavou but the route is not
that nice).
If you head this way, you will also pass a nearby river rapid where you can see
the professionals train or even watch the Canoe slalom world cup.
This cycleway is also suitable for in-line skating.
If you follow the cycleway east from the dormitory, you can get to Libeň. This
way you can almost reach Kaufland, the MFF's building in Karlín or even Malá
Strana, if you do not mind making a little detour.

If you plan to ride a bike, you can borrow bicycle pumps at the reception of
either dormitory building.

If you prefer indoor activities or you just want to exercise during the winter,
you can choose from one of these options:
\begin{itemize}
\item \textbf{Climbing wall} – Lots of students of Matfyz go climbing sometimes.
The nearest climbing wall is called Mamut, if you prefer to climb only small
rock walls without the use of ropes or harnesses, aka bouldering, you should
visit BoulderBar.
Both of them are close to each other, on the other side of the road from
Výstaviště.
\item \textbf{Fitness} – The gym FitInn is located right past the bridge
(Argentinská 38) and it opens from 6:00 a.m. to 24:00 p.m.
FitInn offers various exercising options such as modern machines for cardio and
workout, 15 min circuit training or a separated training space for women.
A 30-day permanent pass costs 499 CZK. There is also a solarium that costs 9
CZK/min.
\item \textbf{Swimming} – The nearest swimming pool is located at Výstaviště.
One hour of swimming costs 50 CZK for students. Aquacentrum Šutka is situated a
bit further, in Kobylisy, and offers a 50m swimming pool (one of the only two
50m swimming pools in Prague -- the other one is located in Podolí but measures
only 49,98 m) plus a waterpark. The prices are also reasonable, especially if
you have a permanent pass.
\item \textbf{Squash} – Squash courts in Prague are mostly low quality (which
means that all walls are usually wooden with the only exception of the back
ones).
You can find such squash court in Holešovice -- Squash-Holešovice. As usual, the
prices for students range from 90 CZK to 290 CZK depending on the time spent
there.
\end{itemize}


\subsubsection{Shops}
Below you can see a list of shops selling mostly groceries. Most of the times
you will probably survive thanks to these.

\subsubsubsection{Karlín}
\begin{itemize}
\item \textit{Billa} near the tram stop Křižíkova in the direction of Florenc.
It is in a comfortable distance from the faculty building.
\item \textit{Billa} between the exit of the metro line C and the tram stop
Florenc.
\item \textit{Albert} across the street from the metro station, past the tram
stop Florenc.
\item \textit{Lidl in Bílá Labuť}, one stop from Florenc in the opposite
direction from that of the buildings of MFF in Karlín.
\end{itemize}

\subsubsubsection{Malá Strana}
\begin{itemize}
\item \textit{Bio-Vacek Mostecká 3} near Karlův most, on the right side of the
street (in the direction of the university). It is a convenient place for buying
snacks, you just need to watch out for the prices -- some of them are too high,
some of them are reasonable.
\item \textit{Žabka Karmelitská 24} about 100 m away from Malostranské náměstí
if you follow the tracks in the direction of Anděl. Also a convenient shop for
buying snacks.
\item \textit{Billa Letenské náměstí} - is not located right at Malá Strana but
near the tram stop Letenské náměstí. The students of Computer Science like to do
the shopping here because they can easily stop by while travelling to the
dormitory.
\item \textit{Albert at Veletržní palác} - from here you can go to Nádraží
Holešovice by the tram no. 6 instead of travelling to Trojská
\end{itemize}

\subsubsubsection{Karlov}
The best shopping options for the students of Mathematics and Physics from
Karlov are at Florenc but of course some shops can be also found in Pavlák.
\begin{itemize}
\item \textit{Žabka Sokolská 31}, near Karlov, not far away from the metro
station.
\end{itemize}

\subsubsubsection{Surroundings of the student residence 17. listopadu}
\begin{itemize}
\item \textit{Kaufland in Libeň} between the stops Palmovka and Libeňský most.
You can get there by the trams no. 3, 8 and 24 from Karlín, by the tram no. 6
from Holešovice, or you can ride a bike on the cycleway along the river.
\item \textit{Tesco Letňany} is located near the bus stop of the buses no. 201
and 911 and never closes.
\item \textit{Small shop for the dormitory residents} on the ground floor of the
building B, right behind the entrance.
\end{itemize}

\subsubsubsection{Another shops that might come in handy}
\begin{itemize}
\item Bookshop of \textit{MatfyzPress} in the MFF's building in Karlín.
\item \textit{Pražská tržnice} in Holešovice, one tram stop away from the metro
line C, station Vltavská. There are a few halls where you can find stalls
selling vegetables and kitchen utensils, grocery shops \textit{Norma} and
\textit{Penny Market}, post office, \textit{Alza} and lots of stalls owned by
Vietnamese.
\item Bookshop \textit{ NeoLuxor} on Václavák. It is a huge bookshop offering a
huge range of goods, such as maps, guides etc.
\item \textit{IKEA} near the metro stations Černý most or Zličín. Very
convenient for buying cheap furniture and accessories -- mirrors, kitchen
utensils, lamps...
\item \textit{Decathlon} not far away from Tesco Letňany (at the other end of
the Letňany shopping center), near the metro station Černý most (in the Černý
most shopping center), near the metro station Zličín (shopping center Metropole
Zličín) or one stop from the metro station Chodov (but this place is difficult
to reach without a car).
It is a sports shop selling swimming suits in winter and gloves in summer. There
is a big choice of sport equipment and clothes.
If you are not looking for the best quality things (you can find these in
special stores), you will get most of the sport equipment you could ever need
here.
\end{itemize}


\subsubsection{Pubs}
Pubs, restaurants, bars and other facilities for quenching one's thirst are one
of the most important parts of the student's life.
It does not matter whether the day is hot, whether you are trying to hide during
storm, from a lecture or a boy/girlfriend, or whether your roommate just gave
you some money in exchange for a free room.
If you do not know what to do during those long winter evenings, you want to
celebrate or you just fancy a drink, go to a pub. There are lots of them in
Prague, you can find one almost everywhere you look, on every street, in every
square.
That actually means that these recommendations (covering the locations most
important for the students of Matfyz) are almost useless, they are meant to be
just an inspiration.
It is up to you whether you want to become a regular or you will rather discover
new and new places and compare.

\subsubsubsection{Student residence 17.listopadu}
The student residence 17. listopadu is a place where most of the students spend
at least a few years. Unfortunately, there are no pubs nearby so you have to
travel a bit if you fancy a drink.
\begin{itemize}
\item The nearest pub with an outside seating is located right at the tram stop
Výstaviště Holešovice. Beer from the brewery Ferdinand from Rakovník is on tap.
It is one stop by tram from Nádraží Holešovice. The beer is good and prices
reasonable.
\item U Houbaře - go by tram to the stop Veletržní palác, then walk a bit along
the tramway and finally you can see it on the left side, at the corner of a
building. They have excellent Pilsner on tap and the food is also good.
Generally speaking, there are many pubs in the vicinity of Veletržní palác, you
do not have to visit this one specifically. There is also the Valcha restaurant
(they have Pilsner on tap, located at the corner between Výstaviště and
Veletržní palác, you cannot miss it), the nonstop bar with Staropramen on tap
(between Houbař and Valcha) or the cheap bar with Gambrinus on tap (below
Houbař).
\item Czech Slovak restaurant - The restaurant U Skřetů is popular not only with
Slovaks who long for traditional Slovak dishes or Slovak beer Zlatý Bažant. You
can find it between the stops Kamenická and Letenské náměstí.
Look for a sign Zlatý Bažant on the right side in the direction of Letenské
náměstí.
\item Another option is to go up to Kobylisy. For example there is a brewery
Cobolis near the metro station Ládví and they sometimes organize tours and
events. You cannot miss it if you exit the metro station in the direction of the
library.
\end{itemize}

\subsubsubsection{Karlov}
There is nothing there. Well, there is, but you have to look more carefully.
The closest pub is called Švejk and it is located right in front of the Main
Central Dispatch at Na bojišti 5, Prague 2. If you go to Pavlák (turn right when
you reach the urology clinic but instead of going through the pedestrian
underpass, take a left), you will pass Kulový Blesk offering a choice from a
wide range of family breweries (e.g. Matuška). Unfortunately both of these are a
bit expensive for students so you will probably look for another options.
One of them is to go through the pedestrian underpass starting at the urology
clinic. You will find two pubs at its end.
Or you can skip the searching altogether and just choose some of the pubs around
the metro station I. P. Pavlova, there are lots of them.
Another option is to visit bar Mrtvá ryba, usually visited by the students of
the Faculty of Science, so there will be many opportunities for meeting new
people. You can usually get beer Černá hora there for a good price.
Locating this place is a bit more difficult -- just Google the address Benátská
4.
Another good pubs are Merlin Irish Pub and Galerka, not far from the dormitory
in Budeč.

\subsubsubsection{Karlín}
It is not very difficult to find a pub in this part of the city so we will just
recommend a few favourite places.
The U Tunelu pub is the easiest to find -- you just pass the metro station
Křižíkova and continue straight ahead, then you will see it on the right side of
the entrance to Žižkovský tunel.
If you like to get to know new beers, stop by the Diego beer bar where they have
up to ten different types of beer from different breweries on tap at one time.
You will get there if you go from the university in the direction of Invalidovna
(which means in the opposite direction than that of Florence), then you will see
it on the right side past the traffic lights. There tend to be lots of people at
the end of the day.
Another pleasant bar with an outside seating is located on the riverbank near
the ferry stop Rohanský ostrov. They have beer Přístav on tap. If you are lucky
and there are not many people, it is a very nice place to work in peace.

\subsubsubsection{Malá Strana}
This part of the city is very popular with the tourists and the prices usually
match that.
Nevertheless you might try out the U Glaubiců restaurant -- exit the building of
Matfyz and turn right, go along the tramway and when you get to the first street
on your right, cross it and continue uphill. You will see it on the left side of
the street.

\subsubsubsection{SCUK Hostivař}
There are two main options in the vicinity of SCUK.
If you go by train (which is often the fastest connection), do not miss the
Hostivařská nádražka bar. Drinking their cheap beer Staropramen while waiting
for a train is a pleasant way of passing the spare time.
The second option also cannot be missed, you can get beer Radegast on your way
from SCUK to the bus stop Gercenova (or on your way there but be careful not to
drink too much before your PE class).


\subsubsection{Tea rooms}
Sometimes you just want to talk with your friends over a cup of high quality
tea, do your homework or relax. Below you can see our recommendations for best
nearby tea rooms.

The Na Cestě tea room is located near the street Ke Karlovu and you will get a
little discount if you have an ISIC card (about 5 \%).
The students of Mathematics from Karlín are close to one of the best tea rooms
in the city called Dharmasala which is situated on Karlínské náměstí. They have
excellent tea and the atmosphere is quiet and calm.
When travelling from Malá Strana to the dormitory, you can visit the U Kostela
tea room located on Strossmayerák but it is unfortunately usually full of the
smoke from shishas.
You can find the cozy Květinová čajovna tea room close to Národní divadlo.
The last tea room we will mention is the U Cesty tea room (do not confuse it
with \uv{Na Cestě}) that can be found in Botanická zahrada.

Lots of the students of Matfyz like to drink high quality tea so it is probably
no surprise that you can meet some of them even in the dormitory.
If you know someone like that or you just saw him/her sitting in the lecture
room with a gaiwan, you can just try to knock on their door and ask for a cup of
tea.


\subsubsection{Other options}
There are lots of other things to do in Prague. You can find numerous cinemas
and theatres -- we will leave it up to you whether you visit or not.
Most of the theatres offer considerable student discounts so it is highly
recommended to look for them. Some of the special student discounts are listed
on the website of Spolek Matfyzák.

If you fancy watching a movie, you can either go to a multicinema or you can
choose from some of the smaller cinemas that usually also offer some less known
movies. The Bio OKO cinema in Holešovice is probably closest to the dormitory.

Last, but not least, you can just choose to spend time with other students of
Matfyz. You can start singing in the Sebranka choir or you can take part in the
evening dancing events.
If you rather organize things, get involved in the organization of a
corresponding seminar or join us in Spolek Matfyzák.
There are also certainly lots of interesting things happening at the dormitory.
If you notice some of them on Facebook or just hear a guitar playing while
walking down the corridor, do not be afraid to join the other people.