\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}   % pro unicode UTF-8
\usepackage[czech]{babel} %jazyk dokumentu
\usepackage{listings}
\usepackage{color}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{listingsutf8}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage[margin={1cm,2cm}]{geometry}

\graphicspath{ {/} }

\def\doubleunderline#1{\underline{\underline{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\noindent
\textbf{Class: AJ III}\\
\textbf{Homework: Survey report}\\
\textbf{Version: 1.}\\
\textbf{Author: David Napravnik}

\section*{Programming languages survey report}
In overal there were varied opinions about programming languages with wide diversity.

\subsection*{Do you prefer imperative or declarative programming languages?}
From the result, we can see, that 50\% of respondents prefer imperative programin language over declarative.\\
So we cannot say which type is better as they both are equaly popular.




\subsection*{What is easiest language to learn programming (upper mean easier)}
The absolute winner is here Python, because everybody choose it as the best programming language to learn programming.\\
Modern languages like C\# and Java were less popolar, but still on very impressive places.\\
Javascript, C and Pascal were mean to be unpopular at all, as they are not good for learning programming.




\subsection*{Which language from these main ones is better}
For this I choosed favourite languages, that are evenly split in the world.\\
Our result is as expected also evenly splitted, that mean our survey was filled with people with different preferencies.



\subsection*{Whych functionality has your favorite language and that is not available elsewhere}
In this question respondet only one person with this:\\
"Java's Reflection API is quite useful for backward compatibility."\\
That mean, that very valuable for programmer is backward compatibility, as they are independent on users version of program executer.




\subsection*{How do you like multiple times nested if else?}
Average was 2.5 from 5, that mean, that people dont like this type of programs, but
there are worster type of programs to read and this principe can be used if its necessary.




\end{document}